---
title: "Bella Beat"
author: "Vishesh Modi"
date: "27/10/2021"
output:
  html_document: default
  pdf_document: default
---

<style type="text/css">
  body{
  font-family: Roboto-Mono;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Libraries used

So the libraries I've used for my case study are tidyverse, lubridate and ggplot

```{r libraries}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(tibble)
options(scipen = 100)
```

### Dataframes

The data frames used to make the analysis has information about dailyActivites, sleepDay merged and weightLogInfo_merged.

```{r df}
setwd("D:/Data Analysis/Case Study - bellaBeat/Fitabase Data 4.12.16-5.12.16")
df1 <- read_csv("dailyActivity_merged.csv")
df2 <- read_csv("sleepDay_merged.csv")
df3 <- read.csv("weightLogInfo_merged.csv")
```
### Some Basic Info about the data frame 1
```{r}
colnames(df1)
head(df1) %>% select(Id, ActivityDate, Calories)
```
### Some Basic Info about the data frame 2
```{r}
colnames(df2)
head(df2) %>% select(Id, SleepDay, TotalHoursAsleep)
```

### Some Basic Info about the data frame 3
```{r}
colnames(df3)
head(df3) %>% select(Id, Date,WeightKg)
```
### Now renaming some column names

```{r}
df1 <- plyr :: rename(df1, c("ActivityDate" = "Date"))
df2 <- plyr :: rename(df2, c("SleepDay" = "Date"))
```
### Drop Unecessary Columns
```{r}
df1 <- select(df1, Id, Date, Calories)
df2 <- select(df2, Id, Date, TotalHoursAsleep)
df3 <- select(df3, Id, Date, WeightKg)
colnames(df1)
colnames(df2)
colnames(df3)
```
### Check for number of rows and unique data
```{r}
n_distinct(df1$Id)
n_distinct(df2$Id)
n_distinct(df3$Id)
```


### Now merging the dataset will help to elimate the extra data
```{r}
df4 <- merge(df2, df1, by = "Id")
df5 <- merge(df4, df3, by = "Id")
head(df5)
```
### Some conversions into categories
```{r}
df5 <- df5 %>% 
  mutate(sleepCategories = case_when(
    TotalHoursAsleep >6 & TotalHoursAsleep <= 8 ~ "6h-8h",
    TotalHoursAsleep > 8 ~ "> 8h",
    TRUE ~ "< 6h"
  ))
```


 
### Some Data Visualizations
```{r}
ggplot(data = df5) + geom_smooth(mapping = aes(x = TotalHoursAsleep, y = WeightKg), color = 'darkgreen') + labs(title = "Comparision of Total Hours Slept VS Weight In Kg", x = "Total Hours Slepts", y = "Weight In KG")

ggplot(data = df5) + geom_col(mapping = aes(x = sleepCategories, y = Calories, fill = sleepCategories)) + labs(title = "Different Categories of Sleeping Time v Calories in KG", x = "Sleep Categories", y = "Calories")

```

### Summary
1. There are two graphs showing relationships of Total Hours Slept v Weight In KG and Sleep categories v Calories burnt.
2. The first one shows that the person who sleeps between 6 - 8hrs is healthier when compared to person who sleeps less           than 6 hrs and more than 8hrs
3. The second one shows that the person who sleeps between between 6 - 8hrs lose burns more calories when compared to person      who sleeps less than 6 hrs and more than 8hrs.

### Recommendations
1. So there's a clear relationship between weight and sleep and calories and sleep, so the app should focus more on giving tips and motivate it's users that why a healthy sleep is required for human body.
2. The app should also feature functions to track sleeping activities like when is the best time to sleep, provide exclusive alarm features to wake up early.


